# Data transformation

```{r, include=FALSE}
# this prevents package loading message from appearing in the rendered version of your problem set
knitr::opts_chunk$set(warning = FALSE, message = FALSE,
                      echo = FALSE)
```

```{r}
library(rvest)
library(robotstxt)
library(tidyverse) 
library(patchwork)
library(naniar)
library(janitor)
library(lubridate)
```

We have several different datasets from Wikipedia. We will divide them into four different sections and do the data transformation separately. Later, we will use these cleaned data to plot and answer our questions in the introduction.

## iPhone Features Data

The dataset of Apple products features is very large, and it contains a lot of information in various aspects. We will mainly focus on certain features (including Release date, Display, Rear Camera) of iPhone for all available models. Firstly, we will merge several tables of different models, and then separate them into smaller tables for different features. 

For release date table, we added another column to store the date information in the correct format.
For the display data table, we will focus on the screen size and the resolution information. We added extra column for screen size in inch, resolution x and resolution y.

```{r}
if (paths_allowed("https://en.wikipedia.org/wiki/List_of_iOS_and_iPadOS_devices")) {
  webdata <- read_html("https://en.wikipedia.org/wiki/List_of_iOS_and_iPadOS_devices")
  table <- webdata %>% html_table()
  iphmodel_inprod <- table[[4]][-1,] 
  iphmodel_dispr<- table[[5]][-1,] 
      
  #Display Info Table
  display1 <- iphmodel_inprod[c(3:20),-1] 
  display2 <- iphmodel_dispr[c(3:21),-1] %>% select(-c(17,18,19))
  display <- full_join(display2,display1) %>% replace_with_na_if(.predicate = is.character, condition = ~.x %in% ("N/A"))
  display[20, 1] = "Typical Max brightness"
  
  #Rear Camera Info table
  rearcam1 <- iphmodel_inprod[c(58:93),-1]
  rearcam2 <- iphmodel_dispr[c(59:94),-1] %>% select(-c(17,18,19))
  rearcam <- inner_join(rearcam2,rearcam1) %>% replace_with_na_if(.predicate = is.character, condition = ~.x %in% ("N/A"))
  rearcam <- rearcam[!duplicated(rearcam), ]
}
```

```{r}
# clean display table
r_display <- data.frame(t(display))
colnames(r_display) <- r_display[1,]
r_display <- tail(r_display, -1) 
r_display <- tibble::rownames_to_column(r_display, "Model")
colnames(r_display) <- gsub(" ", "", colnames(r_display))

r_display <- add_column(r_display, ScreenSizeIn = parse_number(r_display$ScreenSize))
r_display <- add_column(r_display, ResX = parse_number(r_display$Resolution))
r_display <- add_column(r_display, ResY = parse_number(str_sub(r_display$Resolution, start=5)))

r_display <- r_display[-c(2,4,6,12,13,22,24)]
```

```{r}
# clean rear camera table
r_rearcam <- data.frame(t(rearcam))
colnames(r_rearcam) <- r_rearcam[1,]
r_rearcam <- tail(r_rearcam, -1)
r_rearcam <- tibble::rownames_to_column(r_rearcam, "Model")
```

```{r}
if (paths_allowed("https://en.wikipedia.org/wiki/List_of_iOS_and_iPadOS_devices")) {
  webdata2 <- read_html("https://en.wikipedia.org/wiki/List_of_iOS_and_iPadOS_devices")
  table2 <- webdata2 %>% html_table()
  iphGen <- table2[[3]] %>% select(-9)
  
  #release date table
  iph_rel<-iphGen %>% select(c(2,4,5))
  iph_rel <- iph_rel %>% add_column(ReleaseDate = as.Date(str_sub(.$Released, -11, -2)))
  iph_rel <- iph_rel %>% add_column(ReleaseYear = format(.$ReleaseDate, format="%Y"))
  iph_rel <- iph_rel %>% add_column(DisconDate = if_else(.$Discontinued == "In production", Sys.Date(), as.Date((str_sub(.$Discontinued, -11, -2)))))
  
  #supported table
  iph_sup <- iphGen %>% select (c(2,7))
}
```

iPhone Release Date 
```{r}
summary(iph_rel)
```

iPhone Display table
```{r}
summary(r_display)
```

iPhone Rear Camera table
```{r}
summary(rearcam)
```

iPhone supported months table
```{r}
summary(iph_sup)
```

## Apple Finance Data

The finance table includes revenue, net income, total assets, and employees information. However, there are some missing data in the table, so we need to replace the word "N/A" with NA in our dataframe. Also, the value in year column is not in reasonable format, so we also update that.

```{r}
if (paths_allowed("https://en.wikipedia.org/wiki/Apple_Inc.")) {
  webdata <- read_html("https://en.wikipedia.org/wiki/Apple_Inc.")
  table <- webdata %>% html_table()
  financeTable <- table[[4]] %>% replace_with_na_if(.predicate = is.character, condition = ~.x %in% ("N/A"))
}
financeTable <- financeTable %>% mutate(Year=as.character.Date(substring(.$Year, 0, 4)))
summary(financeTable)
```


## Customer Satisfaction Data

Initially, we want to use the data from [this page](https://www.macrumors.com/2020/05/19/apple-smartphone-customer-satisfaction-index/), but the format of the data is picture instead of tables. Then we found [this table](https://www.theacsi.org/acsi-benchmarks/benchmarks-by-brand/benchmarks-for-smartphones) with the same information, and we extracted the table from here and modified the column names.

```{r}
if (paths_allowed("https://www.theacsi.org/acsi-benchmarks/benchmarks-by-brand/benchmarks-for-smartphones")) {
  csdata <- read_html("https://www.theacsi.org/acsi-benchmarks/benchmarks-by-brand/benchmarks-for-smartphones")
  table <- csdata %>% html_table()
  cstable <- table[[1]]
  colnames(cstable) <- cstable[2,]
  cstable <- tail(cstable, -2)
}
summary(cstable)
```

## Comparison with Samsung Galaxy S Smartphones



