# Results

```{r, include=FALSE}
# this prevents package loading message from appearing in the rendered version of your problem set
knitr::opts_chunk$set(warning = FALSE, message = FALSE,
                      echo = FALSE)
```

```{r}
library(rvest)
library(robotstxt)
library(tidyverse) 
library(patchwork)
library(naniar)
library(janitor)
library(vistime)
```

## Different iPhone Features Changing

First of all, we will analyze several different features of all models of iPhones.

### Release and Discontinued Date
According to the cleaned table of released and discontinued data table, we plot this timeline 
```{r}
vistime(iph_rel, col.event="Model", col.start = "ReleaseDate", col.end = "DisconDate", optimize_y = TRUE)
```

```{r}
ggplot(iph_rel, aes(x=ReleaseYear)) +
  geom_bar() +
  ggtitle("Number of iPhone Models Released in Each Year")
```

According to these two plots, we are able to see that Apple gradually introduced more and more products over the year. 

### iPhone Display Table

```{r}
library(parcoords)
parcoords(r_display
          , brushMode = "1D-axes"
          , reorderable = T
          , queue = T
          , color = list(
            colorScale = "scaleOrdinal"
            ,colorScheme = "schemeCategory10"
          )
          , withD3 = TRUE)

```

Interactive parallel coordinates plot for display???????????

```{r}
r_display %>%
  ggplot(aes(x=fct_inorder(Model), y=ScreenSizeIn)) +
  # geom_smooth(formula = y ~ x, method = "lm") + ???????
  geom_point() +
  theme(axis.text.x=element_text(angle=60,hjust = 1)) +
  ggtitle("iPhone Screen Size (in) of Different Models")
```

```{r}
r_display %>% 
  ggplot(aes(x=ResX, y=ResY)) +
  geom_point() +
  geom_text(aes(label=Model), hjust=0, vjust=0) +
  # check_overlap???? avoid overlap? less model okay?
  ggtitle("iPhone Resolution of Different Models")
```



### iPhone Rear Camera Table


### Supported Date Table ???? 


## Apple Fianance Data Analysis


## Customer Satisfaction

Apple and Samsung together dominated the individual brand rankings, and 17 of the 18 models that earned a score of 80 or above came from either Samsung or Apple.


## Smartphones Comparison