# Results

```{r, include=FALSE}
# this prevents package loading message from appearing in the rendered version of your problem set
knitr::opts_chunk$set(warning = FALSE, message = FALSE,
                      echo = FALSE)
```

```{r}
library(rvest)
library(robotstxt)
library(tidyverse) 
library(patchwork)
library(naniar)
library(janitor)
library(vistime)
```

## Different iPhone Features Changing

In order for us to better understand how products are changing to suit the public’s varying needs, it is necessary to examine the change of products’ features over the year. As an iconic figure among all Apple products, iPhone can be a typical product for our analysis. In this section, we will take deep analysis on the features of different generations of iPhone products, like the release date and discontinued date, display of the phone, and the rear camera mode. In our data cleaning section, we have obtained the data that contain those essential information, and we will utilize these data and a vast of R libraries including tidyverse, rvest, robotstxt, patchwork, naniar, janitor, and vistime to help our exploratory analysis. 

### Release and Discontinued Date
According to the cleaned table of released and discontinued data table, we plot this timeline 
```{r}
vistime(iph_rel, col.event="Model", col.start = "ReleaseDate", col.end = "DisconDate", optimize_y = TRUE)
```

```{r}
ggplot(iph_rel, aes(x=ReleaseYear)) +
  geom_bar() +
  ggtitle("Number of iPhone Models Released in Each Year")
```

According to these two plots, we are able to see that Apple gradually introduced more and more products over the year. 

### iPhone Display Table

```{r}
library(parcoords)
library(d3r)
library(RColorBrewer)

cleanNA_display <- r_display
cleanNA_display[is.na(cleanNA_display)] <- "NA"
colnames(cleanNA_display) <- abbreviate(names(cleanNA_display), minlength=5)

parcoords(cleanNA_display
          , rownames = F
          , brushMode = "1D-axes"
          , reorderable = T
          , queue = T
          , color = list(
            colorScale = "scaleOrdinal"
            ,colorScheme = "schemeCategory10"
          )
          , withD3 = TRUE)

```

We have selected some features from the origianl iPhone Display table.
Column names explanation??? 

```{r}
r_display %>%
  ggplot(aes(x=1:nrow(r_display), y=ScreenSizeIn)) +
  #ggplot(aes(fct_inorder(Model), y=ScreenSizeIn))+
  geom_point() +
  geom_smooth(formula = y ~ x, method = "lm", se = FALSE) +
  #scale_x_continuous(Model) +????
  #theme(axis.text.x=element_text(angle=60,hjust = 1)) +
  xlab("iPhone Models (in order of release time)") +
  ggtitle("iPhone Screen Size (in) of Different Models")
```

Ignore the x-axis values. The x-axis value for each point is each iPhone model in the order of release time. 


```{r}
r_display %>% 
  ggplot(aes(x=ResX, y=ResY)) +
  geom_point() +
  geom_text(aes(label=Model), hjust=0.5, vjust=-0.5, check_overlap=T) +
  ggtitle("iPhone Resolution of Different Models")
```

(We checked the overlap models, and only keep one of them.)


### iPhone Rear Camera Table
For iPhone Rear Camera, we mainly care about some features as the following.
```{r}
part_rearcam <- r_rearcam[, c('Model', 'Aperture', 'Night Mode', 'Flash', 'Video Recording', 'Optical Image Stabilization')]
part_rearcam
```


## Apple Fianance Data Analysis

```{r}
#??
```


## Customer Satisfaction

Apple and Samsung together dominated the individual brand rankings, and 17 of the 18 models that earned a score of 80 or above came from either Samsung or Apple.


## Smartphones Comparison

